---
title: "Example Usage"
author: "Yilin Liu"
date: "2/21/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(xtable)
source("./basket.R")
source("./single_stg_anal.R")
```

### Overview

This document shows an example of computing operating characteristics for a local-MEM trial with fixed design for 4 baskets. The simulation is performed in `prior_sensitivity_analysis.R`. Here we directly load the simulation data and calculate basket-wise/trial-wise metrics.

### Prior settings:

Let $|\Omega_j|$ be the number of blocks in partition j.

* Setting 1: no preference over partitions

$$
\pi(\Omega_{j}) = \frac{|\Omega_j|^0}{\sum_{j}|\Omega_j|^0} = \frac{1}{J}
$$

* Setting 2

$$
\pi(\Omega_{j}) = \frac{|\Omega_j|^1}{\sum_{j}|\Omega_j|^1}
$$

* Setting 3

$$
\pi(\Omega_{j}) = \frac{|\Omega_j|^2}{\sum_{j}|\Omega_j|^2}
$$

### 4 baskets

#### $p_0=0.15$ for all

```{r}
load("./data/B4_0.15_0.15_0.15_0.15.RData")
pmat
```

```{r}
b4_part_mat <- cbind(part, n_bk, prior_mat)
b4_part_mat
print(xtable(b4_part_mat,
             digits=c(rep(0, 5), rep(3, 4))),
      scalebox = 0.9,
      include.colnames=TRUE,
      include.rownames=FALSE)
```


```{r}
# ---- Summarize local MEM results ----
mem_eval1 <- mem_eval(mem_pp, pmat, target=0.099)
```

```{r}
mem_b4_homo <- NULL

for (i in 1:3) {
  colnames(mem_eval1[[i]])[ncol(mem_eval1[[i]])] <- "FWER"
  mem_b4_homo <- rbind(mem_b4_homo, mem_eval1[[i]])
}
# mem_b4_homo

rownames(mem_b4_homo) <- rep(c(paste(c(0:B), "Success")), 3)
mem_b4_homo
```

#### Uniform prior for independent analysis


```{r}
uni_pp <- array(NA, dim = c(nrow(pmat), nsim, B))

for(j in 1:nrow(pmat)){
  ptrue <- pmat[j, ]
  for(i in 1:nsim){
    set.seed(i)
    x <- rbinom(B, size = Nvec, prob = ptrue)
    y <- Nvec - x
    uni_pp[j, i , ] <- 1 - pbeta(p0, 1+x, 1+y)
  }
}
# power for basket-wise analysis with beta(1,1) prior
uni_pow <- matrix(NA, nrow = nrow(pmat), ncol = B)

# find posterior thereshold maintaining the FWER at target
gam <- fwer1(post_prob = uni_pp[1, , ], fwer_target = target)$gam
uni_fwer <- NULL
for(j in 1:nrow(pmat)){
  pp <- uni_pp[j, , ]
  uni_pow[j, ] <- colMeans(pp>gam)
  uni_fwer[j] <- fwer1(post_prob = matrix(pp[, pmat[j, ]==p0], nrow=nsim),
              gam = gam)$FWER
}

b4_homo_uni <- cbind(uni_pow, uni_fwer)
b4_homo_uni
```

